\large UNet-HCRF Integration for Sequence Labeling on EEG Data

### 2024-12-09 manuscript/slides.tex
edit experiment

\section[Data Preprocessing]{Data Preprocessing}

\begin{frame}{Data Preparation}
\begin{itemize}
\item Extract the 10 min long Kaggle Spectrogram centered at the middle time
where the experts rating (Global EEGs)
\item Transform the 50s long EEG waveforms into Spectrograms
\end{itemize}
\end{frame}

\begin{frame}{EEG signal denosing using Wavelet transform}
\begin{footnotesize}
\begin{align*}
& \text{LL Spec} = \frac{1}{4} \left[
spec(Fp1-F7) + spec(F7-T3) + spec(T3-T5) + spec(T5-O1) \right], \\
& \text{LP Spec} = \frac{1}{4} \left[
spec(Fp1-F3) + spec(F3-C3) + spec(C3-P3) + spec(P3-O1) \right], \\
& \text{RP Spec} = \frac{1}{4} \left[
spec(Fp2-F4) + spec(F4-C4) + spec(C4-P4) + spec(P4-O2) \right], \\
& \text{RR Spec} = \frac{1}{4} \left[
spec(Fp2-F8) + spec(F8-T4) + spec(T4-T6) + spec(T6-O2) \right]
\end{align*}
\end{footnotesize}
\begin{figure}[tbp]
\centering
\includegraphics[width=.55\textwidth]{inion}
\end{figure}
\end{frame}

\begin{frame}{EEG Signal Denosing using Wavelet Transform}
\begin{enumerate}
\item Calculates the mean absolute deviation of a signal $d$:
\begin{equation*}
\mathrm{maddest}(d, axis) = \frac{1}{N} \sum_{i=1}^N
\left\vert d_i - \frac{1}{N} \sum_{j=1}^N d_j \right\vert,
\end{equation*}
where $d_i$ is the value of the signal at index $i$, and
$N$ is the length of $d$.
\item Denoises a signal using wavelet decomposition:
\begin{enumerate}
\item Perform wavelet decomposition
\item Calculate the noise standard deviation using the last level of
coefficients
\item Compute the universal threshold
\item Apply a hard thresholding operation to the coefficients
\item Reconstruct the signal using the inverse wavelet transform
\end{enumerate}
\end{enumerate}
\end{frame}

\begin{frame}{Create Spectrograms from the Middle 50 Seconds}
\begin{figure}[tbp]
\centering
\includegraphics[width=.4\textwidth]{EEG_Signal}
\end{figure}
\begin{figure}[tbp]
\centering
\includegraphics[width=.5\textwidth]{EEG_Spectrogram}
\end{figure}
\end{frame}

>>>>

\section[Experiment]{Experiment}

\begin{frame}{Harmful Brain Activity Classification Dataset}
\begin{itemize}
\item The dataset contains 50-second long electroencephalography (EEG) samples
covering a 10-minute window as well as spectrograms matching each sample.
\bigskip
\item The EEG samples were labeled by expert annotators to determine which of
the six features each spectrogram belonged to.
\bigskip
\item The longer 10-minute window allows for the model to pick up on further
insights regarding the nature of the brain activity.
\end{itemize}
\end{frame}

\begin{frame}{Data Preparation}
\begin{itemize}
\item Extract 10-minute long spectrograms centered at the midpoint time,
where the expert ratings (Global EEGs) were provided.
\bigskip
\item Convert the 50-second long EEG waveforms into spectrograms.
\end{itemize}
\end{frame}

\begin{frame}{Make Spectrogram from EEG}
\begin{itemize}
\item Bipolar Montage combines multiple EEG electrode signals by calculating
the difference between adjacent electrodes, yielding signals representing
specific brain regions.
\end{itemize}
\begin{figure}[tbp]
\centering
\includegraphics[width=.7\textwidth]{inion}
\end{figure}
\end{frame}

\begin{frame}{Make Spectrogram from EEG (cont.)}
\begin{itemize} 
\item A single time series signal is required to generate a spectrogram.
To create four spectrograms from the dataset's 19 EEG time series signals,
we employ Bipolar Montage to combine them into four representative signals.
\end{itemize}
\begin{footnotesize}
\begin{align*}
& \text{LL Spec} = \frac{1}{4} \left[
spec(Fp1-F7) + spec(F7-T3) + spec(T3-T5) + spec(T5-O1) \right], \\
& \text{LP Spec} = \frac{1}{4} \left[
spec(Fp1-F3) + spec(F3-C3) + spec(C3-P3) + spec(P3-O1) \right], \\
& \text{RP Spec} = \frac{1}{4} \left[
spec(Fp2-F4) + spec(F4-C4) + spec(C4-P4) + spec(P4-O2) \right], \\
& \text{RR Spec} = \frac{1}{4} \left[
spec(Fp2-F8) + spec(F8-T4) + spec(T4-T6) + spec(T6-O2) \right],
\end{align*}
\end{footnotesize}
where $spec(\cdot)$ is a custom function implemented using the \pkg{pywt} and
\pkg{librosa} packages for signal transformation.
\end{frame}

%\begin{frame}{EEG Signal Denosing using Wavelet Transform}
%\begin{enumerate}
%\item Calculates the mean absolute deviation of a signal $d$:
%\begin{equation*}
%\mathrm{maddest}(d, axis) = \frac{1}{N} \sum_{i=1}^N
%\left\vert d_i - \frac{1}{N} \sum_{j=1}^N d_j \right\vert,
%\end{equation*}
%where $d_i$ is the value of the signal at index $i$, and
%$N$ is the length of $d$.
%\item Denoises a signal using wavelet decomposition:
%\begin{enumerate}
%\item Perform wavelet decomposition
%\item Calculate the noise standard deviation using the last level of
%coefficients
%\item Compute the universal threshold
%\item Apply a hard thresholding operation to the coefficients
%\item Reconstruct the signal using the inverse wavelet transform
%\end{enumerate}
%\end{enumerate}
%\end{frame}

\begin{frame}{Make Spectrogram from EEG (cont..)}
\begin{figure}[tbp]
\centering
\vspace{-.5em}
\includegraphics[width=.5\textwidth]{EEG_Signal}
\end{figure}
\vspace{-1em}
\begin{figure}[tbp]
\centering
\includegraphics[width=.55\textwidth]{EEG_Spectrogram}
\end{figure}
\end{frame}
